---
title: "Write up Linear Model"
author: "Salena Bennett"
date: "3/23/2021"
output: 
    html_document:
        toc: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 

You can import the data directly from a link to its website.  Copy that link to the clipboard by right clicking on Raw Data and then copy link.

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)


```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

# model1
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
### Now add in scatterplot

```{r}
basicNN + geom_point()
```
 
Scatter plot shows positive relation between ARM and SIM. Equation of the line is SIMS = -4.1+0.05*ARM.The adjusted R square is 0.467. The residual standard error is 1.226, the residual standard error is it the standard deviation of the normal spread of errors any point on the line.
  

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
### Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

```{r}
newdata=data.frame(GRIP=94,ARM=88)
predict(model.1,newdata,interval="prediction")
```


### now add the model fit to our plot
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 
  
The equation for SIMS explained by ARM is  
SIMS=-4.1+.0545*ARM
The scatter plot shows positive relation between SIMS and ARM. The equation 

# model2
```{r}
basicGG <- ggplot(data,aes(y=SIMS,x=GRIP))
```
### Now add in scatterplot

```{r}
basicGG + geom_point()+geom_smooth(method=lm)
```

The scatter plot shows that there is a positive relation between GRIP and SIM. Equation of the line is SIMS = -4.9 + 0.04 * GRIP. The adjusted R square is 0.405. The residual standard error is 1.295, the residual standard error is the standard deviation of the normal spread of errors any error point on the line.  
  

### Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```
### Inferential  (Build linear model)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
predict(model.2,newdata,interval="prediction")
```


### now add the model fit to our plot
  




  


### Inferential  (Build linear model)
  
# model3




```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
predict(model.3,newdata,interval="prediction")
```
SIMS=-5.43+0.037 * ARM + 0.024 * GRIP 
  
# Compare the models  

```{r}
anova(model.1,model.3)
predict(model.3, newdata, interval = "prediction")
```

The anova compares model 1 with model 3. The null hypothesis is no difference in the ability to predict SIMS. The alternative hypothesis is that there is a difference. The p-value is 0.000005 this is so small the the difference the ability to predict SIMS is not due to chance. The adjusted r square and standard deviation of the errors both indicate the ARM+GRIP model is better. The prediction for ARM+GRIP model is a 0.15 and the 95% confidence interval is -2.1 to 2.4.